### 2024-12-22 paper.tex
docs: setting up the paper
Signed-off-by: Thomas Mauran <thomasmauran@yahoo.com>

\documentclass[12pt,a4paper]{article}

% Packages
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{cite}
\usepackage{geometry}
\geometry{margin=1in}

% Title and Author
\title{How do amateur photometric observations of binary star transits compare in precision and reliability to data collected by professional astronomers?}
\author{Thomas Mauran \\\small Polytech Montpellier  \\\small thomas.mauran@etu.umontpellier.fr}
\date{\today}

\begin{document}

% Title Page
\maketitle

% Abstract
\begin{abstract}
Amateur astronomers have increasingly contributed to astronomical research through advancements in affordable equipment and accessible software. This paper investigates the precision and reliability of photometric observations of binary star transits conducted by amateur astronomers compared to data collected by professional observatories. We analyze case studies, compare methodologies, and assess the implications for collaborative scientific research.
\end{abstract}

% Keywords
\textbf{Keywords:} photometry, binary star systems, amateur astronomy, professional astronomy, data comparison

% Introduction
\section{Introduction}
In recent years, the field of astronomy has witnessed a growing collaboration between amateur and professional astronomers. The advent of high-quality, low-cost equipment has enabled amateur astronomers to perform sophisticated observations, including photometric studies of binary star transits. This paper focuses on photometric observations of the U Cepheihei (U Cephei) binary star system conducted by the author using personal equipment from a Bortle 7 location. The study aims to examine the precision and reliability of these amateur observations in comparison to professional datasets, exploring the potential for collaboration and the challenges inherent in combining data from diverse sources.

% Methodology
\section{Methodology}
To address the research question, this study employs a comparative analysis of photometric data. Observations of the U Cephei binary star system were conducted using personal equipment under urban light pollution conditions (Bortle 7). The following steps were undertaken:
\begin{enumerate}
    \item Setup of observation equipment, including a CCD camera and a telescope with an aperture suitable for photometric studies.
    \item Observation of the U Cephei binary system taking 15 second exposure every 2 minutes.
    \item Acquisition of professional data on U Cephei from observatory archives and published studies for comparison.
    \item Standardization of data formats for comparative analysis.
    \item Statistical evaluation of precision, including signal-to-noise ratios and error margins.
    \item Reliability assessment through consistency checks and cross-validation with established models.
\end{enumerate}

% Equipment
\section{equipment}
Specifying the equipment used in the study is essential to understanding the context and limitations of the observations. 
I employed the following equipment for the photometric observations of U Cephei:

\begin{itemize}
    \item Telescope: Sky-Watcher Quattro 150P Newtonian reflector telescope with a 150mm aperture and 600mm focal length.
    \item Reducer: Sky-Watcher 0.85x Coma Corrector lowering the focal length to 510mm.
    \item Camera: ZWO ASI 585MC pro monochrome CCD camera with a 8.29 MP sensor.
    \item Filters: UV and IR cut filter for reducing light pollution and enhancing contrast.
    \item Mount: Celestron Celestrong cg-5 goto equatorial mount for tracking and guiding.
    \item Software: N.I.N.A for image acquisition and PHD2 guiding software for tracking. AstroImageJ for data analysis.
    \item Light Pollution: Montpellier, Bortle 7 (suburban/urban transition) location with moderate light pollution.
\end{itemize}

% Star sytem
\section{U Cephei Binary Star System}
U Cephei is a well-known binary star system located in the constellation Cepheus. The system consists of a white 
% Results
\section{Results}
The analysis reveals both strengths and limitations in the amateur photometric observations of U Cephei:
\begin{itemize}
    \item Amateur data demonstrated significant precision in detecting transit features, with signal-to-noise ratios that were competitive with professional datasets under optimal conditions.
    \item Light pollution and equipment limitations introduced variability, leading to slightly higher error margins compared to professional datasets.
    \item Cross-validation with professional data confirmed the overall reliability of the amateur observations, with minor deviations attributed to observational conditions.
\end{itemize}
Figures and tables summarizing the comparative results are presented below.

% Discussion
\section{Discussion}
% The findings underscore the feasibility of conducting meaningful photometric observations of binary star systems, such as U Cephei, under suboptimal conditions using personal equipment. While light pollution (Bortle 7) posed challenges, careful calibration and consistent methodology mitigated many of the issues. The results demonstrate the potential for amateur observations to complement professional studies, particularly for systems with frequent or well-documented transits.

% This study highlights the potential of amateur astronomers to contribute to the broader astronomical community. By focusing on specific systems like U Cephei, amateurs can provide valuable data to supplement professional observations. Future efforts should aim to enhance equipment calibration techniques and explore automated tools for improving data reliability.

% Conclusion
\section{Conclusion}
The personal photometric observations of U Cephei conducted in this study illustrate the potential for amateur astronomers to achieve a high degree of precision, even in light-polluted environments. These observations, while slightly less precise than professional datasets, offer valuable insights and demonstrate the viability of citizen science in advancing binary star research. Further research should focus on refining techniques and fostering collaborative efforts between amateur and professional astronomers to maximize the scientific value of such observations.

% References
\begin{thebibliography}{99}
\bibitem{example1} Smith, J., "Photometric Studies of Binary Stars," \textit{Astrophysical Journal}, vol. 123, no. 4, pp. 567-578, 2020.
\bibitem{example2} Brown, A., \textit{Amateur Contributions to Astronomy}, Cambridge University Press, 2018.
\bibitem{example3} Doe, R., "Comparative Analysis of Amateur and Professional Astronomical Data," \textit{Astronomy and Astrophysics}, vol. 456, no. 3, pp. 234-245, 2019.
\end{thebibliography}

\end{document}

### 2024-12-25 paper.tex
docs: writting
Signed-off-by: Thomas Mauran <thomasmauran@yahoo.com>

@@
 
+% skip to the next page
+\newpage
+
+% Table of Contents
+\tableofcontents
+
 % Introduction
 \section{Introduction}
-In recent years, the field of astronomy has witnessed a growing collaboration between amateur and professional astronomers.
-The advent of high-quality, low-cost equipment has enabled amateur astronomers to perform sophisticated observations, including photometric studies of binary star transits.
-This paper focuses on photometric observations of the U Cepheihei (U Cephei) binary star system conducted by the author using personal equipment from a Bortle 7 location.
-The study aims to examine the precision and reliability of these amateur observations in comparison to professional datasets, exploring the potential for collaboration and the challenges inherent in combining data from diverse sources.
+In recent years, the field of astronomy has witnessed a growing collaboration between amateur 
+and professional astronomers. The advent of high-quality, low-cost equipment has enabled 
+amateur astronomers to perform sophisticated observations, including photometric studies of 
+binary star transits. This paper focuses on photometric observations of the U Cephei 
+(U Cephei) binary star system conducted by the author using personal equipment from a 
+Bortle 7 location. The study aims to examine the precision and reliability of these amateur 
+observations in comparison to professional datasets, exploring the potential for collaboration
+and the challenges inherent in combining data from diverse sources.
+
+% Problematic
+\subsection{Problematic}
+
+% State of the Art
+\section{State of the Art}
+The field of photometric observation has witnessed significant advancements due to improvements in both professional and amateur technologies.
+
+\section{What are transits?}
+
+Transits are a phenomenon that occurs when a celestial body passes in front of another, partially or totally blocking its light.
+Those events are very interesting for astronomers as they can provide a lot of information about the objects involved, such as their size, mass, and even atmosphere.
+
+The first exoplanet was discovered using the transit method, and it's still one of the most used methods to detect exoplanets.
+One of the way to know if a star is part of a binary system is to observe it and see if it's light intensity varies over time, which can be a sign of a transit event.
+
+\section{On the U Cephei system}
+
+U Cephei is a very interesting binary star system and a great pick to try catching transit eclipses.
+
+\subsection{Why U Cephei?}
+
+There are multiple reasons why U Cephei is a great candidate for me in this study.
+
+\subsubsection{Period}
+
+First of all U Cephei period is 2.493 days, which is quite short and allows for multiple chances to observe it on a short period of time. 
+Even though this period seems short since it's not exactly 3 days but 2 and a half it means that one observation out of 2 will be at night and the other during the day.
+Making observation nights possible every 5 days.
+Considering the fact weather conditions are critical for this field, managing to have a night with good seeing condition can also be a challenge, so having multiple chances to observe the same system is a great advantage.
+
+\subsubsection{Eclipse duration}
+
+Secondly, this system eclipse is short, lasting only a couple of hours it's possible in one night to observe the complete eclipse, which is not the case for all binary systems.
+
+\subsubsection{Magnitude variation}
+
+Stars magnitude define how bright they are.
+This scale of magnitude is logarithmic, meaning that a difference of 1 magnitude is a difference of 2.512 times in brightness and a difference of 2 magnitudes is a difference of \(\mathbf{2.512^2}\) times in brightness.
+the scale is inverted, meaning that the lower the magnitude, the brighter the star is.
+
+The magnitude of U Cephei varies from 6.7 to 9.2. Which is actually a huge variation in brightness. If we wanna have a comparaison in percentage we can do the following calculation:
+
+We can right the magnitude variation as a ratio of brightness variation:
+
+\begin{equation}
+     2.512^{m_2-m_1} = \frac{F_1}{F_2}
+\end{equation}
+
+\begin{equation}
+    2.512^{9.2-6.7} \approx 10
+\end{equation}
+
+In other words, during the transit, U Cephei will be 10 times less bright than when it's not in transit. This is a huge variation and makes it easier to detect the transit.
+
+\subsubsection{Data availability}
+
+Finally, U Cephei is a well-known system, with a lot of data available from professional observatories, which makes it a great candidate for me as an amateur astronomer to try to catch some transits and compare my data to the professional ones.
 

### 2024-12-25 python-scripts/fourrier.py

@@ -1,0 +1,20 @@
+import matplotlib.pyplot as plt
+import pandas as pd
+
+# Load the CSV data into a DataFrame
+data = pd.read_csv("data.csv")
+
+# Display the first few rows
+# print(data.head())
+
+# Check for missing values
+# print(data.isnull().sum())
+# Count occurrences of each type
+type_counts = data['type'].value_counts()
+
+# Pie chart
+plt.figure(figsize=(8, 6))
+type_counts.plot.pie(autopct='%1.1f%%', startangle=140, cmap='Pastel1')
+plt.ylabel("")
+plt.title("Supernova Type Distribution")
+plt.show()

### 2024-12-31 paper.tex
docs: add light curve and stuff
Signed-off-by: Thomas Mauran <thomasmauran@yahoo.com>

@@
 % Title and Author
-\title{How do amateur photometric observations of binary star transits compare in precision and reliability to data collected by professional astronomers?}
+\title{Assessing the Scientific Value of Amateur Photometric Observations of Binary Star Transits}
 \author{Thomas Mauran \\\small Polytech Montpellier  \\\small thomas.mauran@etu.umontpellier.fr}
@@
 
-% skip to the next page
 \newpage
@@
 \tableofcontents
+
+\newpage
 
@@
 
-% State of the Art
-\section{State of the Art}
-The field of photometric observation has witnessed significant advancements due to improvements in both professional and amateur technologies.
+\medskip
+
+% bold 
+\textbf{How do amateur photometric observations of binary star transits compare in precision and reliability to data collected by professional astronomers, and is data collected by amateurs precise enough to contribute to science?}
 
@@
 % Equipment
-\section{equipment}
+\subsection{Equipment used}
 Specifying the equipment used in the study is essential to understanding the context and limitations of the observations. 
@@
     \item Filters: UV and IR cut filter for reducing light pollution and enhancing contrast.
-    \item Mount: Celestron Celestrong cg-5 goto equatorial mount for tracking and guiding.
+    \item Mount: Celestron Celestrong cg-5 goto equatorial mount for trackin.
+    \item Autoguider: ZWO ASI 120MM mini monochrome camera and 50mm guide scope for guiding.
     \item Software: N.I.N.A for image acquisition and PHD2 guiding software for tracking. AstroImageJ for data analysis.
@@
 
-% Star sytem
-\section{U Cephei Binary Star System}
-U Cephei is a well-known binary star system located in the constellation Cepheus. The system consists of a white 
 % Results
 \section{Results}
-The analysis reveals both strengths and limitations in the amateur photometric observations of U Cephei:
+
+\subsection{Light curve}
+
+The first thing to do after collecting the data is to plot it and see if we can see any transit event.
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.8\textwidth]{imgs/light-curve.png}
+    \caption{Light curve of U Cephei showing a clear transit event.}
+    \label{fig:light_curve}
+\end{figure}
+
+On the x axis we have the time of the observation in Julian Date (JD), and on the y axis we have the relative flux of the stars.
+
+To understand a bit more those scales I think it is important to take the time to explain each of them.
+\begin{itemize}
+    \item Relative flux: In astronomy the light emited by a star is measured in flux, which is the amount of light received per unit area. Here we are dealing with \textit{normalized relative flux}. 
+    The relative flux is basically the flux of a star compared to other, it is very important in out case because of some pertubations that could affect the light received by the camera, such as clouds, or the moon or the atmosphere.
+    \begin{equation}
+        \text{Relative Flux} = \frac{\text{Flux of the Target Star}}{\text{Flux of the Comparison Star}}
+    \end{equation}
+
+    We also normalize the data to have a relative flux of 1 when the star is not in transit, this way we can see the variation of the flux during the transit.
+    \item Julian Date: The Julian Date is a continuous count of days since the beginning of the Julian Period on January 1, 4713 BC. 
+    It is widely used in astronomy because it is a continuous count of days, allowing for easy comparison of dates and times.
+\end{itemize}
+
+\subsection{Conclusion}
+
 \begin{itemize}

### 2025-01-02 paper.tex
docs: adding documentation and scripts
Signed-off-by: Thomas Mauran <thomasmauran@yahoo.com>

@@
 \usepackage{geometry}
+\usepackage{hyperref}
+\usepackage{float}
+
 \geometry{margin=1in}
@@
 observations in comparison to professional datasets, exploring the potential for collaboration
-and the challenges inherent in combining data from diverse sources.
+and the challenges inherent in combining data from diverse sources. The final goal of the study if it is 
+successful enough is to submit the collected data to the AAVSO (American Association of Variable Star Observers).
 
@@
 % bold 
-\textbf{How do amateur photometric observations of binary star transits compare in precision and reliability to data collected by professional astronomers, and is data collected by amateurs precise enough to contribute to science?}
+\textbf{How do amateur photometric observations of binary star transits compare in precision and reliability to data collected by professional astronomers, and is this collected data precise enough to contribute to science?}
 
@@
 
+\subsection{Cleaning the data}
+
+The first step in analyzing the data is to clean it, this means removing any outliers or bad data points that could affect the results but also in our case making sure our star is aligned on each frame to make the process easier.
+
+\bigskip
+
+% TODO : Add a before and after image of the data cleaning process
+
+Using \href{https://siril.org/fr/}{Siril} which is a free and opensource software for astrophotography, it is very easy to align all the images of the observation to make sure the star is always at the same place in the frame.
+As a comparaison here is the same data after the cleaning process:
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\textwidth]{imgs/aligned.png}
+    \caption{Cleaned data of U Cephei.}
+    \label{fig:cleaned_data}
+\end{figure}
+
+Here is an example aligned image after the Siril process, we can see that the software shifted
+the frame to align the star in the sme way on all the images. During the process,
+each image had to be debayered before being aligned, this process is called preprocessing.
+
+\bigskip
+
+Basically when taking pictures with a CCD camera, the sensor is covered with a Bayer filter which is a color filter array, this means that each pixel of the sensor is covered with a red, green or blue filter.
+The process of debayering is to reconstruct the image by interpolating the missing colors of each pixel, this is done to get a full color image.
+
+\medskip
+
+After cleaning the data I wanted to see if it was possible to detect the transit event just by creating a video of the frames.
+Since this eclipse variation of magnitude is so important I felt like it could be visible enough.
+
+\bigskip
+
+Using a python script I converted each of the fit file into a grayscale png and then was able to use the ffmpeg library to create a video of the frames.
+The result is available \href{https://youtube.com/shorts/rVnEccCb3Aw}{here}.
+
+In it we can cleary see the star getting dimmer until the frame 150 and then brighter again, this is the transit event happening.
+
 \subsection{Light curve}
 
-The first thing to do after collecting the data is to plot it and see if we can see any transit event.
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=0.8\textwidth]{imgs/light-curve.png}
-    \caption{Light curve of U Cephei showing a clear transit event.}
-    \label{fig:light_curve}
-\end{figure}
-
-On the x axis we have the time of the observation in Julian Date (JD), and on the y axis we have the relative flux of the stars.
+After our data has been collected and prepared we can plot a light curve which is a graph showing the variation of the flux of the star over time.
+On the x axis we will have the time of the observation in Julian Date (JD), and on the y axis we have the relative flux of the stars.
 
@@
 \end{itemize}
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.8\textwidth]{imgs/light-curve.png}
+    \caption{Light curve of U Cephei showing a clear transit event.}
+    \label{fig:light_curve}
+\end{figure}
+
+The light curve of U Cephei is showing a clear transit event happening, we can see the flux of the star decreasing and then increasing again, as comparaison to the flux of the comparison star.
+
+Only 2 comparision stars are showcased on this graph, but in reality 7 comparision stars were used to get a more accurate result.
+When looking at their light curve we clearly see that they remain pretty stable throughout the observation,
+and normalized around 1, which is a good sign that the data is reliable.
+
+This is a great result, it means that the observation was successful and that we managed to catch a transit event, now it is time to compare it to data that was collected by professional observatories.
+
+\subsection{Comparative Analysis}
 

### 2025-01-02 python-scripts/grayscale_fit_convert.py

@@ -1,0 +1,67 @@
+import os
+from astropy.io import fits
+import numpy as np
+from datetime import datetime, timedelta
+import csv
+
+# Directories
+input_dir = "./img/"
+output_dir = "./grayscale"
+os.makedirs(output_dir, exist_ok=True)
+
+# Starting datetime: 24th December 2024, 18:30
+start_time = datetime(2024, 12, 24, 18, 30)
+frame_interval = timedelta(minutes=2)
+
+# Calibration CSV file
+calibration_file = os.path.join(output_dir, "timestamps.csv")
+
+# Open the calibration file for writing
+with open(calibration_file, mode='w', newline='') as file:
+
+    # Process each FITS file
+    for index, filename in enumerate(sorted(os.listdir(input_dir))):  # Sort to process frames in order
+        if filename.endswith(".fit"):
+            filepath = os.path.join(input_dir, filename)
+            
+            # Open the FITS file
+            with fits.open(filepath) as hdul:
+                data = hdul[0].data  # Assuming the image data is in the first HDU
+                
+                # Inspect the shape of the data
+                print(f"Processing {filename}, data shape: {data.shape}")
+                
+                # Handle 3D data by collapsing to 2D
+                if len(data.shape) == 3:
+                    data = np.mean(data, axis=0)  # Take mean across the first dimension
+                
+                # Replace NaN values with zero
+                data = np.nan_to_num(data)
+                
+                # Normalize the data to 0-255 for image conversion (optional if needed)
+                norm_data = (data - np.min(data)) / (np.max(data) - np.min(data)) * 255
+                norm_data = norm_data.astype(np.uint8)  # Convert to 8-bit integer
+                
+                # Calculate the target timestamp
+                target_time = start_time + index * frame_interval
+                
+                # Create a new FITS file with the same data but with the timestamp in the header
+                output_path = os.path.join(output_dir, filename.replace(".fit", "_modified.fit"))
+                
+                # Create a new HDU (Header Data Unit) with the image data
+                hdu = fits.PrimaryHDU(norm_data)
+                
+                # Add timestamp to the header (using a custom keyword)
+                hdu.header['DATE-OBS'] = target_time.isoformat()  # Standard date keyword
+                hdu.header['TIMESTAMP'] = target_time.isoformat()  # Custom timestamp keyword
+                
+                # Write the new FITS file
+                hdu.writeto(output_path, overwrite=True)
+                
[…]

### 2025-01-02 python-scripts/plot-differences/main.py

@@ -1,0 +1,67 @@
+import pandas as pd
+import matplotlib.pyplot as plt
+import numpy as np
+
+# Load the data
+ucep = pd.read_csv('./ucep.csv', delimiter=';')
+tess = pd.read_csv('./tess.csv')
+
+# Inspect the data
+print(ucep.head())  
+print(ucep.columns)
+
+# Extract relevant columns
+ucep_time = ucep['JD_UTC']  # Time from ucep.csv
+ucep_flux = ucep['rel_flux_T1']  # Relative flux for target star
+
+tess_time = tess['time']  # Time from tess.csv
+tess_mag = tess['mag']  # Magnitude from TESS
+
+# Trim TESS data to match U Cephei's timeframe
+ucep_start = ucep_time.min()
+ucep_end = ucep_time.max()
+tess_trimmed = tess[3130:3185]
+
+# Update TESS variables after trimming
+tess_time = tess_trimmed['time']
+tess_mag = tess_trimmed['mag']
+
+# Convert U Cephei flux to magnitude
+ucep_mag = -2.5 * np.log10(ucep_flux)
+
+# Interpolate U Cephei data to match TESS times
+ucep_interp_mag = np.interp(tess_time, ucep_time, ucep_mag)
+
+# Calculate the difference in magnitude
+mag_diff = ucep_interp_mag - tess_mag
+
+# Plot the light curves and their difference
+plt.figure(figsize=(12, 8))
+
+# Plot TESS light curve
+plt.subplot(3, 1, 1)
+plt.plot(tess_time, tess_mag, label='TESS Magnitude', color='blue')
+plt.gca().invert_yaxis()  # Magnitudes are inverted (brighter is lower)
+plt.ylabel('Magnitude')
+plt.title('TESS Light Curve')
+plt.legend()
+
+# Plot U Cephei light curve
+plt.subplot(3, 1, 2)
+plt.plot(ucep_time, ucep_mag, label='U Cephei Magnitude', color='orange')
+plt.gca().invert_yaxis()
+plt.ylabel('Magnitude')
+plt.title('U Cephei Light Curve')
+plt.legend()
+
+# Plot the difference
+plt.subplot(3, 1, 3)
+plt.plot(tess_time, mag_diff, label='Difference (U Cephei - TESS)', color='green')
+plt.axhline(0, color='red', linestyle='--')
+plt.xlabel('Time')
+plt.ylabel('Magnitude Difference')
[…]

### 2025-01-02 python-scripts/png_grayscale.py

@@ -1,0 +1,95 @@
+import os
+from astropy.io import fits
+import numpy as np
+from PIL import Image, ImageDraw, ImageFont
+
+# Directories
+input_dir = "./img/"
+png_dir = "./png"
+os.makedirs(png_dir, exist_ok=True)
+
+# Parameters for cropping
+crop_size = 1000  # Crop dimensions (1000x1000)
+center_x, center_y = 2250, 750  # Adjust to your desired center coordinates
+
+# Gamma correction function
+def gamma_correction(image, gamma=1.0):
+    norm_image = image / 255.0
+    corrected_image = np.power(norm_image, gamma)
+    return (corrected_image * 255).astype(np.uint8)
+
+# Crop function
+def crop_center(image, center_x, center_y, crop_size):
+    half_size = crop_size // 2
+    start_x = max(center_x - half_size, 0)
+    start_y = max(center_y - half_size, 0)
+    end_x = start_x + crop_size
+    end_y = start_y + crop_size
+    return image[start_y:end_y, start_x:end_x]
+
+# Font settings for frame number overlay
+try:
+    font_path = "/usr/share/fonts/truetype/dejavu/DejaVuSans-Bold.ttf"  # Adjust if necessary
+    font = ImageFont.truetype(font_path, 50)
+except:
+    print("Warning: Font not found, using default font.")
+    font = ImageFont.load_default()  # Fallback font
+
+# Process each FITS file
+for index, filename in enumerate(sorted(os.listdir(input_dir))):  # Sort to process frames in order
+    if filename.endswith(".fit"):
+        filepath = os.path.join(input_dir, filename)
+        
+        try:
+            # Open the FITS file
+            with fits.open(filepath) as hdul:
+                data = hdul[0].data  # Assuming the image data is in the first HDU
+                
+                # Use the frame number as the overlay text
+                frame_number = f"Frame {index + 1}"  # Frame number starts at 1
+                
+                # Handle 3D data by summing along the first dimension
+                if len(data.shape) == 3:
+                    data = np.sum(data, axis=0)
+                
+                # Replace NaN values with zero
+                data = np.nan_to_num(data)
+                
+                # Normalize the data to 0-255 for image conversion
+                norm_data = (data - np.min(data)) / (np.max(data) - np.min(data)) * 255
+                norm_data = norm_data.astype(np.uint8)
+                
+                # Apply gamma correction
+                bright_data = gamma_correction(norm_data, gamma=0.4)
+                
[…]

### 2025-01-04 paper.tex
docs: adding more accurate curves and comparisons
Signed-off-by: Thomas Mauran <thomasmauran@yahoo.com>

@@
     \centering
-    \includegraphics[width=0.8\textwidth]{imgs/aligned.png}
+    \includegraphics[width=0.8\textwidth]{assets/aligned.png}
     \caption{Cleaned data of U Cephei.}
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{imgs/light-curve.png}
+    \includegraphics[width=1\textwidth]{assets/Measurements.png}
     \caption{Light curve of U Cephei showing a clear transit event.}
@@
 The light curve of U Cephei is showing a clear transit event happening, we can see the flux of the star decreasing and then increasing again, as comparaison to the flux of the comparison star.
+I didn't completely trim the data after the transit to showcase the return to normal of the star, we see that from 0.62 to the end the curve seems to stabilize again and become linear.
 
-Only 2 comparision stars are showcased on this graph, but in reality 7 comparision stars were used to get a more accurate result.
-When looking at their light curve we clearly see that they remain pretty stable throughout the observation,
+Only 2 comparision stars are showcased on this graph, but in reality 7 comparision stars were picked to get a more accurate result.
+When looking at those 2 light curve we clearly see that they remain pretty linear throught the night,
 and normalized around 1, which is a good sign that the data is reliable.
+The pertubations on the light curves can be explained by the fact that the stars are not at the same altitude in the sky, and that the atmosphere can affect the light received by the camera, as well as the fact
+this data is collected by an amateur setup.
+
+We also can notive a small gap in the data around the meridian flip since this is not fully automated yet, the telescope had to be flipped manually, which caused a small gap in the data.
+
+\bigskip
 
@@
 \subsection{Comparative Analysis}
+
+To validate the reliability of the amateur observations, I conducted a comparative analysis with professional data from the Transiting Exoplanet Survey Satellite (TESS) mission.
+The TESS data provided a benchmark for evaluating the precision and accuracy of the amateur observations.
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=1\textwidth]{assets/comparaison.png}
+    \caption{Light curve comparaison from TESS data and amateur data.}
+    \label{fig:light_curve}
+\end{figure}
+
+One thing we see when looking at those light curves is the fact they are not overlapping.
+This can be explained by the fact that TESS is in space and doesn't have to deal with the atmosphere, making the star looks brighter.
+It could also be explained by the fact
+TESS sensor is more sensitive than the one used in this study, making the star looks brighter.
+This is why the data is not overlapping, but the transit event is still clearly visible on both light curves.
 
@@
 Figures and tables summarizing the comparative results are presented below.
-
-% Discussion
-\section{Discussion}
-% The findings underscore the feasibility of conducting meaningful photometric observations of binary star systems, such as U Cephei, under suboptimal conditions using personal equipment.
-While light pollution (Bortle 7) posed challenges, careful calibration and consistent methodology mitigated many of the issues.
-The results demonstrate the potential for amateur observations to complement professional studies, particularly for systems with frequent or well-documented transits.
 

### 2025-01-04 python-scripts/change_timestamp.py

@@ -1,0 +1,45 @@
+import os
+import csv
+import re
+from datetime import datetime
+
+# Path to the CSV file
+csv_file = "processed_data.csv"
+
+# Path to the folder containing images
+image_folder = "data/"
+
+# Read the CSV and create a mapping of image_number to datetime
+image_timestamps = {}
+with open(csv_file, mode='r', encoding='utf-8') as file:
+    reader = csv.DictReader(file)
+    for row in reader:
+        image_number = int(row["image_number"])
+        datetime_str = row["datetime"]
+        image_timestamps[image_number] = datetime.strptime(datetime_str, "%Y-%m-%d %H:%M:%S")
+
+# Regex pattern to extract the number from the image filenames (with leading zeros)
+filename_pattern = re.compile(r"r_u_cephei_(\d+)\.fit$")
+
+# Iterate through the image files in the folder
+for filename in os.listdir(image_folder):
+    match = filename_pattern.match(filename)
+    if match:
+        image_number = int(match.group(1))  # Convert extracted number to integer to match CSV
+        if image_number in image_timestamps:
+            # Get the corresponding timestamp
+            new_timestamp = image_timestamps[image_number]
+            
+            # Construct the full file path
+            file_path = os.path.join(image_folder, filename)
+            
+            # Change the file's timestamp
+            timestamp_unix = new_timestamp.timestamp()
+            os.utime(file_path, (timestamp_unix, timestamp_unix))
+            print(f"Updated timestamp for {filename} to {new_timestamp}")
+        else:
+            print(f"No matching timestamp found for {filename}")
+    else:
+        print(f"Filename does not match pattern: {filename}")
+
+print("Timestamp update process complete.")

### 2025-01-04 python-scripts/fourrier.py

@@ -1,20 +1,0 @@
-import matplotlib.pyplot as plt
-import pandas as pd
-
-# Load the CSV data into a DataFrame
-data = pd.read_csv("data.csv")
-
-# Display the first few rows
-# print(data.head())
-
-# Check for missing values
-# print(data.isnull().sum())
-# Count occurrences of each type
-type_counts = data['type'].value_counts()
-
-# Pie chart
-plt.figure(figsize=(8, 6))
-type_counts.plot.pie(autopct='%1.1f%%', startangle=140, cmap='Pastel1')
-plt.ylabel("")
-plt.title("Supernova Type Distribution")
-plt.show()

### 2025-01-04 python-scripts/grayscale_fit_convert.py

@@ -1,67 +1,76 @@
 import os
 from astropy.io import fits
 import numpy as np
-from datetime import datetime, timedelta
 import csv
+from datetime import datetime
+import re
 
 # Directories
-input_dir = "./img/"
-output_dir = "./grayscale"
+input_dir = "./data/"
+output_dir = "./grayscale/"
 os.makedirs(output_dir, exist_ok=True)
 
-# Starting datetime: 24th December 2024, 18:30
-start_time = datetime(2024, 12, 24, 18, 30)
-frame_interval = timedelta(minutes=2)
+# CSV file with timestamps
+timestamp_csv = "processed_data.csv"
 
-# Calibration CSV file
-calibration_file = os.path.join(output_dir, "timestamps.csv")
+# Load timestamps from CSV into a dictionary
+timestamps = {}
+with open(timestamp_csv, mode='r', encoding='utf-8') as file:
+    reader = csv.DictReader(file)
+    for row in reader:
+        image_number = int(row["image_number"])
+        timestamps[image_number] = datetime.strptime(row["datetime"], "%Y-%m-%d %H:%M:%S")
 
-# Open the calibration file for writing
-with open(calibration_file, mode='w', newline='') as file:
+# Process each FITS file
+for filename in sorted(os.listdir(input_dir)):  # Sort to process frames in order
+    if filename.endswith(".fit"):
+        # Extract the image number from the filename
+        match = re.match(r"r_u_cephei_(\d+)\.fit$", filename)
+        if match:
+            image_number = int(match.group(1))
+            if image_number in timestamps:
+                original_time = timestamps[image_number]
+                filepath = os.path.join(input_dir, filename)
 
-    # Process each FITS file
-    for index, filename in enumerate(sorted(os.listdir(input_dir))):  # Sort to process frames in order
-        if filename.endswith(".fit"):
-            filepath = os.path.join(input_dir, filename)
-            
-            # Open the FITS file
-            with fits.open(filepath) as hdul:
-                data = hdul[0].data  # Assuming the image data is in the first HDU
-                
-                # Inspect the shape of the data
-                print(f"Processing {filename}, data shape: {data.shape}")
-                
-                # Handle 3D data by collapsing to 2D
-                if len(data.shape) == 3:
-                    data = np.mean(data, axis=0)  # Take mean across the first dimension
-                
-                # Replace NaN values with zero
-                data = np.nan_to_num(data)
-                
[…]

### 2025-01-04 python-scripts/plot-differences/main.py

@@ -3,31 +3,43 @@ import matplotlib.pyplot as plt
 import numpy as np
 
 # Load the data
-ucep = pd.read_csv('./ucep.csv', delimiter=';')
+ucep = pd.read_csv('./Measurements.csv', delimiter=';')
+ucep = ucep[0:263]
+
 tess = pd.read_csv('./tess.csv')
+tess_trimmed = tess[38:102]
+
 
 # Inspect the data
-print(ucep.head())  
+print(ucep.head())
 print(ucep.columns)
 
 # Extract relevant columns
-ucep_time = ucep['JD_UTC']  # Time from ucep.csv
-ucep_flux = ucep['rel_flux_T1']  # Relative flux for target star
+ucep_time = ucep['JD_UTC']
+for i in range(len(ucep_time)):
+    ucep_time[i] = ucep_time[i] - 2460669 # We need to subtract the first value from all the values to get the correct time
+ucep_mag = ucep['Source_AMag_T1']
 
-tess_time = tess['time']  # Time from tess.csv
-tess_mag = tess['mag']  # Magnitude from TESS
+for i in range(len(ucep_mag)):
+    ucep_mag[i] = ucep_mag[i] - 0.5
+
+tess_time = tess['time']
+
+for i in range(len(tess_time)):
+    tess_time[i] = tess_time[i] - 2744
+
+tess_mag = tess['mag']
 
 # Trim TESS data to match U Cephei's timeframe
 ucep_start = ucep_time.min()
 ucep_end = ucep_time.max()
-tess_trimmed = tess[3130:3185]
 
 # Update TESS variables after trimming
 tess_time = tess_trimmed['time']
 tess_mag = tess_trimmed['mag']
 
 # Convert U Cephei flux to magnitude
-ucep_mag = -2.5 * np.log10(ucep_flux)
+# ucep_mag = -2.5 * np.log10(ucep_flux) + 7
 
 # Interpolate U Cephei data to match TESS times
 ucep_interp_mag = np.interp(tess_time, ucep_time, ucep_mag)
@@ -38,29 +50,31 @@ mag_diff = ucep_interp_mag - tess_mag
 # Plot the light curves and their difference
 plt.figure(figsize=(12, 8))
 
+# Split light curves in 2 graphs 
 # Plot TESS light curve
-plt.subplot(3, 1, 1)
-plt.plot(tess_time, tess_mag, label='TESS Magnitude', color='blue')
+# plt.subplot(3, 1, 1)
[…]

### 2025-01-04 python-scripts/png_grayscale.py

@@ -4,7 +4,7 @@ import numpy as np
 from PIL import Image, ImageDraw, ImageFont
 
 # Directories
-input_dir = "./img/"
+input_dir = "./data/"
 png_dir = "./png"
 os.makedirs(png_dir, exist_ok=True)
 

### 2025-01-04 python-scripts/timestamp_extractor.py

@@ -1,0 +1,48 @@
+import re
+import csv
+
+# File containing the data
+input_file = "conversion.txt"
+
+# Read data from the file
+with open(input_file, "r", encoding="utf-8") as file:
+    data = file.read()
+
+# Define a regular expression to extract the necessary fields
+pattern = r"'(.*?)' -> '(.*?)' image (\d+)"
+
+# Extract matches
+matches = re.findall(pattern, data)
+
+# Create a structured list for further processing
+processed_data = []
+for match in matches:
+    file_path, sequence_file, image_number = match
+    
+    # Extract date and time from the file path (assumes format YYYY-MM-DD_HH-MM-SS exists in the path)
+    date_time_match = re.search(r'(\d{4}-\d{2}-\d{2})_(\d{2}-\d{2}-\d{2})', file_path)
+    if date_time_match:
+        exact_date = date_time_match.group(1)  # Extract date (YYYY-MM-DD)
+        exact_time = date_time_match.group(2).replace("-", ":")  # Extract time (HH:MM:SS)
+        exact_datetime = f"{exact_date} {exact_time}"  # Combine date and time
+    else:
+        exact_datetime = "Unknown"
+
+    processed_data.append({
+        "datetime": exact_datetime,
+        "sequence_file": sequence_file,
+        "image_number": int(image_number)
+    })
+
+# Example output to verify results
+for entry in processed_data[:10]:  # Print the first 10 entries as a sample
+    print(entry)
+
+# Save to a CSV file for analysis (optional)
+output_file = "processed_data.csv"
+with open(output_file, mode='w', newline='', encoding='utf-8') as file:
+    writer = csv.DictWriter(file, fieldnames=["datetime", "sequence_file", "image_number"])
+    writer.writeheader()
+    writer.writerows(processed_data)
+
+print(f"Data saved to {output_file}")

### 2025-01-05 paper.tex
docs: refactor and improvements
Signed-off-by: Thomas Mauran <thomasmauran@yahoo.com>

@@
 
-% Problematic
-\subsection{Problematic}
+\section{What are transits?}
 
-\medskip
-
-% bold 
-\textbf{How do amateur photometric observations of binary star transits compare in precision and reliability to data collected by professional astronomers, and is this collected data precise enough to contribute to science?}
-
-\section{What are transits?}
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=1\textwidth]{assets/star-transits.jpg}
+    \caption{Transit of binary star system schema and associated light curves.}
+    \label{fig:transits}
+\end{figure}
 
@@
 
-In other words, during the transit, U Cephei will be 10 times less bright than when it's not in transit. This is a huge variation and makes it easier to detect the transit.
+In other words, during the transit, U Cephei will be 10 times dimmer than when it's not in transit. This is a huge variation and makes it easier to detect the transit.
 
@@
 The following steps were undertaken:
-\begin{enumerate}
-    \item Setup of observation equipment, including a CCD camera and a telescope with an aperture suitable for photometric studies.
-    \item Observation of the U Cephei binary system taking 15 second exposure every 2 minutes.
-    \item Acquisition of professional data on U Cephei from observatory archives and published studies for comparison.
-    \item Standardization of data formats for comparative analysis.
-    \item Statistical evaluation of precision, including signal-to-noise ratios and error margins.
-    \item Reliability assessment through consistency checks and cross-validation with established models.
-\end{enumerate}
 
-% Equipment
-\subsection{Equipment used}
+\subsection{Observation Setup}
+
 Specifying the equipment used in the study is essential to understanding the context and limitations of the observations. 
@@
     \item Autoguider: ZWO ASI 120MM mini monochrome camera and 50mm guide scope for guiding.
-    \item Software: N.I.N.A for image acquisition and PHD2 guiding software for tracking. AstroImageJ for data analysis.
+    \item Software: N.I.N.A for image acquisition and PHD2 guiding software for tracking. AstroImageJ for data analysis and Siril for aligning the images.
     \item Light Pollution: Montpellier, Bortle 7 (suburban/urban transition) location with moderate light pollution.
@@
 
-% Results
-\section{Results}
+\subsection{Observation Procedure}
 
-\subsection{Cleaning the data}
+\subsection{Cleaning the amateur data}
 
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{assets/aligned.png}
-    \caption{Cleaned data of U Cephei.}
+    \includegraphics[width=1\textwidth]{assets/aligned.png}
+    \caption{Cleaned data of U Cephei and it's comparison stars used for the study.}
     \label{fig:cleaned_data}
@@
 Here is an example aligned image after the Siril process, we can see that the software shifted
-the frame to align the star in the sme way on all the images. During the process,
+the frame to align the star in the same way on all the images. During the process,
 each image had to be debayered before being aligned, this process is called preprocessing.
@@
 In it we can cleary see the star getting dimmer until the frame 150 and then brighter again, this is the transit event happening.
+
+\subsection{Professional Data Acquisition}
+
+\subsection{Standardization of Data Formats, light curves and comparative analysis}
+
+% Results
+\section{Results}
 
@@
 
-\subsection{Conclusion}
-
 \begin{itemize}
@@
 Future efforts should aim to enhance equipment calibration techniques and explore automated tools for improving data reliability.
+
+\section{Discussion}
 

### 2025-01-05 python-scripts/plot-differences/main.py

@@ -7,7 +7,8 @@ ucep = pd.read_csv('./Measurements.csv', delimiter=';')
 ucep = ucep[0:263]
 
 tess = pd.read_csv('./tess.csv')
-tess_trimmed = tess[38:102]
+# tess_trimmed = tess[38:102]
+tess_trimmed = tess[3118:3192]
 
 
 # Inspect the data
@@ -17,7 +18,8 @@ print(ucep.columns)
 # Extract relevant columns
 ucep_time = ucep['JD_UTC']
 for i in range(len(ucep_time)):
-    ucep_time[i] = ucep_time[i] - 2460669 # We need to subtract the first value from all the values to get the correct time
+    ucep_time[i] = ucep_time[i] - 2460669
+
 ucep_mag = ucep['Source_AMag_T1']
 
 for i in range(len(ucep_mag)):
@@ -26,7 +28,7 @@ for i in range(len(ucep_mag)):
 tess_time = tess['time']
 
 for i in range(len(tess_time)):
-    tess_time[i] = tess_time[i] - 2744
+    tess_time[i] = tess_time[i] - 2766.46
 
 tess_mag = tess['mag']
 

### 2025-01-07 paper.tex
docs: plots
Signed-off-by: Thomas Mauran <thomasmauran@yahoo.com>

@@
     \item Reducer: Sky-Watcher 0.85x Coma Corrector lowering the focal length to 510mm.
-    \item Camera: ZWO ASI 585MC pro monochrome CCD camera with a 8.29 MP sensor.
+    \item Camera: ZWO ASI 585MC pro monochrome CMOS camera with a 8.29 MP sensor.
     \item Filters: UV and IR cut filter for reducing light pollution and enhancing contrast.
@@
 
-Here is an example aligned image after the Siril process, we can see that the software shifted
-the frame to align the star in the same way on all the images. During the process,
-each image had to be debayered before being aligned, this process is called preprocessing.
+This screenshot has been taken in AstroImageJ, which is a software used to analyze astronomical images and easily create light curves.
+Here we can see in green my star of interest U Cephei, and in red the comparison stars used to normalize the data.
+You can see that next to each star there is a number, this is the magnitude of the star, which is a measure of its brightness.
 
@@
 
-Basically when taking pictures with a CCD camera, the sensor is covered with a Bayer filter which is a color filter array, this means that each pixel of the sensor is covered with a red, green or blue filter.
-The process of debayering is to reconstruct the image by interpolating the missing colors of each pixel, this is done to get a full color image.
+I chose manually the stars and took them because they have a known magnitude, allowing the software to guess the magnitude of U Cephei.
+To know the magnitude of those reference stars I used the \href{https://apps.aavso.org/vsp/chart/?star=U+Cep&fov=120.0&maglimit=12.0}{AAVSO website} which is a great tool to get information about stars and their magnitude.
+
+By searching for U Cephei you basically get a chart of the star and the stars around it, with their magnitude, which is very useful to pick the right stars for the study.
+
+\bigskip
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\textwidth]{assets/ucep-stars-mag.png}
+    \caption{AAVSO Star chart of U Cephei and neighbors star magnitudes.}
+    \label{fig:Ucep-stars-chart}
+\end{figure}
+
+\bigskip
+
+It's important to note something else in the \ref{fig:cleaned_data} image, we see that the frame has been shifted, this is what Siril did to make sure each frame is aligned.
 
@@
 
-\begin{figure}[h]
+\begin{figure}[H]
     \centering
@@
 To validate the reliability of the amateur observations, I conducted a comparative analysis with professional data from the Transiting Exoplanet Survey Satellite (TESS) mission.
-The TESS data provided a benchmark for evaluating the precision and accuracy of the amateur observations.
 
-\begin{figure}[h]
+\begin{figure}[H]
     \centering
@@
     \caption{Light curve comparaison from TESS data and amateur data.}
-    \label{fig:light_curve}
+    \label{fig:tess-data-comparaison}
 \end{figure}

### 2025-01-07 python-scripts/plot-differences/main.py

@@ -3,59 +3,43 @@ import matplotlib.pyplot as plt
 import numpy as np
 
 # Load the data
-ucep = pd.read_csv('./Measurements.csv', delimiter=';')
+ucep = pd.read_csv('./Measurements-good-time.csv', delimiter=';')
 ucep = ucep[0:263]
 
-tess = pd.read_csv('./tess.csv')
-# tess_trimmed = tess[38:102]
-tess_trimmed = tess[3118:3192]
+tess = pd.read_csv('./tess-2024-good.csv')
 
-
-# Inspect the data
-print(ucep.head())
-print(ucep.columns)
-
-# Extract relevant columns
-ucep_time = ucep['JD_UTC']
-for i in range(len(ucep_time)):
-    ucep_time[i] = ucep_time[i] - 2460669
-
+# Extract relevant columns and adjust time/magnitude
+ucep_time = ucep['UNIX_Timestamp']
 ucep_mag = ucep['Source_AMag_T1']
 
-for i in range(len(ucep_mag)):
-    ucep_mag[i] = ucep_mag[i] - 0.5
-
-tess_time = tess['time']
-
-for i in range(len(tess_time)):
-    tess_time[i] = tess_time[i] - 2766.46
-
+tess_time = tess['Unix_Timestamp']
 tess_mag = tess['mag']
 
-# Trim TESS data to match U Cephei's timeframe
-ucep_start = ucep_time.min()
-ucep_end = ucep_time.max()
+# Check the time ranges for overlap
+print(f"U Cephei time range: {ucep_time.min()} to {ucep_time.max()}")
+print(f"TESS time range: {tess_time.min()} to {tess_time.max()}")
 
-# Update TESS variables after trimming
-tess_time = tess_trimmed['time']
-tess_mag = tess_trimmed['mag']
+# Normalize both U Cephei and TESS times
+ucep_normalized_time = ucep_time - ucep_time.min()
+tess_normalized_time = tess_time - tess_time.min()
 
-# Convert U Cephei flux to magnitude
-# ucep_mag = -2.5 * np.log10(ucep_flux) + 7
 
-# Interpolate U Cephei data to match TESS times
-ucep_interp_mag = np.interp(tess_time, ucep_time, ucep_mag)
+# Interpolate U Cephei magnitudes to match TESS times
+ucep_interp_mag = np.interp(tess_normalized_time, ucep_normalized_time, ucep_mag)
 
-# Calculate the difference in magnitude
[…]

### 2025-01-07 python-scripts/time-converter-csv/convert-my-csv-time.py

@@ -1,0 +1,28 @@
+import pandas as pd
+from astropy.time import Time
+import argparse
+
+# Set up command-line argument parsing
+parser = argparse.ArgumentParser(description='Convert JD_UTC in a CSV file to UNIX timestamp.')
+parser.add_argument('input_file', type=str, help='Path to the input CSV file')
+parser.add_argument('output_file', type=str, help='Path to the output CSV file')
+args = parser.parse_args()
+
+# Load the data
+input_file = args.input_file
+output_file = args.output_file
+data = pd.read_csv(input_file, delimiter=';')  # Adjust delimiter if needed
+
+# Convert JD_UTC to UNIX timestamp
+time_obj = Time(data['JD_UTC'], format='jd', scale='utc')
+data['UNIX_Timestamp'] = time_obj.unix  # Add new column with UNIX timestamp
+
+# Rearrange columns, placing UNIX_Timestamp before JD_UTC
+cols = list(data.columns)
+cols.insert(cols.index('JD_UTC'), 'UNIX_Timestamp')
+data = data[cols]
+
+# Save to a new CSV file
+data.to_csv(output_file, index=False, sep=';')  # Use the same delimiter as the input
+
+print(f"Converted CSV saved as: {output_file}")

### 2025-01-07 python-scripts/time-converter-csv/convert-tess-csv-time.py

@@ -1,0 +1,30 @@
+import pandas as pd
+from astropy.time import Time
+import argparse
+
+# Set up command-line argument parsing
+parser = argparse.ArgumentParser(description='Convert BJD time in a CSV file to Unix timestamp.')
+parser.add_argument('input_file', type=str, help='Path to the input CSV file')
+parser.add_argument('output_file', type=str, help='Path to the output CSV file')
+args = parser.parse_args()
+
+# Load the data
+input_file = args.input_file
+output_file = args.output_file
+data = pd.read_csv(input_file)
+
+# Convert the BJD time to Julian Date
+bjd_base = 2457000.0
+data['JD'] = data['time'] + bjd_base
+
+# Convert Julian Date to Unix timestamp
+time_obj = Time(data['JD'], format='jd', scale='utc')
+data['Unix_Timestamp'] = time_obj.unix  # Add new column with Unix timestamp
+
+# Rearrange columns and drop the old JD column
+data = data[['Unix_Timestamp', 'time', 'mag', 'mag_err']]
+
+# Save to a new CSV file
+data.to_csv(output_file, index=False)
+
+print(f"Converted CSV saved as: {output_file}")

### 2025-01-08 paper.tex
docs: resuts
Signed-off-by: Thomas Mauran <thomasmauran@yahoo.com>

@@
 
-The magnitude of U Cephei varies from 6.7 to 9.2. Which is actually a huge variation in brightness. If we wanna have a comparaison in percentage we can do the following calculation:
+The magnitude of U Cephei varies from 6.7 to 9.2. Which is actually a huge variation in brightness. If we wanna have a comparison in percentage we can do the following calculation:
 
@@
 Using \href{https://siril.org/fr/}{Siril} which is a free and opensource software for astrophotography, it is very easy to align all the images of the observation to make sure the star is always at the same place in the frame.
-As a comparaison here is the same data after the cleaning process:
+As a comparison here is the same data after the cleaning process:
 
@@
 
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=1\textwidth]{assets/Measurements.png}
+    \caption{Light curve of U Cephei showing a clear transit event.}
+    \label{fig:light_curve}
+\end{figure}
+
+In this graph, we see multiple lines: the blue one represents the normalized relative flux of U Cephei, while the red and green ones show the normalized relative flux of the comparison stars.
+The flux of the comparison stars remains fairly linear around 1,
+whereas the flux of U Cephei follows a parabolic curve, starting from 1.5, decreasing to 0.6, and then returning to 1.5 over 9.6 hours.
+This duration is calculated as \( 0.7 - 0.3 = 0.4 \, \text{days} \), and \( 0.4 \, \text{days} \times 24 = 9.6 \, \text{hours} \).
+
+\medskip
+
+We also can notive a small gap in the data around the meridian flip since this is not fully automated yet, the telescope had to be flipped manually, which caused a small gap in the data.
+
+\bigskip
+
+\subsection{Comparative Analysis}
+
+To validate the reliability of the amateur observations, I conducted a comparative analysis with professional data from the Transiting Exoplanet Survey Satellite (TESS) mission.
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=1\textwidth]{assets/comparison.png}
+    \caption{Light curve comparison from TESS data and amateur data.}
+    \label{fig:tess-data-comparison}
+\end{figure}
+
+This graphs shows the light curve of U Cephei from the TESS data in blue and the amateur data I collected in orange. 
+Both curves display a parabolic similar shape.
+The TESS data light curve actually being a bit brighter, starting around 6.85 and lowering to almost 8.25 than the amateur one, starting at 7.75 and lowering to 8.75.
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=1\textwidth]{assets/shifted-comparison.png}
+    \caption{Light curve comparison where the amateur data was shifted by -0.5.}
+  \label{fig:tess-data-comparison-shifted}
+\end{figure}
+
+This is another light curve comparison very similar to the previous one, but this time the amateur data has been shifted by -0.5.
+
+% This study highlights the potential of amateur astronomers to contribute to the broader astronomical community.
+By focusing on specific systems like U Cephei, amateurs can provide valuable data to supplement professional observations.
+Future efforts should aim to enhance equipment calibration techniques and explore automated tools for improving data reliability.
+
+\section{Discussion}
+
+\subsection{Figure 1}
+
 After our data has been collected and prepared we can plot a light curve which is a graph showing the variation of the flux of the star over time.
@@
 
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=1\textwidth]{assets/Measurements.png}
-    \caption{Light curve of U Cephei showing a clear transit event.}
-    \label{fig:light_curve}
-\end{figure}
+The light curve of U Cephei is showing a clear transit event happening.
 
-The light curve of U Cephei is showing a clear transit event happening, we can see the flux of the star decreasing and then increasing again, as comparaison to the flux of the comparison star.
-I didn't completely trim the data after the transit to showcase the return to normal of the star, we see that from 0.62 to the end the curve seems to stabilize again and become linear.
+This is a great result, it means that the observation was successful and that we managed to catch a transit event, now it is time to compare it to data that was collected by professional observatories.
+\medskip
 
@@
 
-We also can notive a small gap in the data around the meridian flip since this is not fully automated yet, the telescope had to be flipped manually, which caused a small gap in the data.
-
-\bigskip
-
-This is a great result, it means that the observation was successful and that we managed to catch a transit event, now it is time to compare it to data that was collected by professional observatories.
-
-\subsection{Comparative Analysis}
-
-To validate the reliability of the amateur observations, I conducted a comparative analysis with professional data from the Transiting Exoplanet Survey Satellite (TESS) mission.
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=1\textwidth]{assets/comparaison.png}
-    \caption{Light curve comparaison from TESS data and amateur data.}
-    \label{fig:tess-data-comparaison}
-\end{figure}
-
+\subsection{Figure 2}
 One thing we see when looking at those light curves is the fact they are not overlapping.
@@
 
-\begin{itemize}
-    \item Amateur data demonstrated significant precision in detecting transit features, with signal-to-noise ratios that were competitive with professional datasets under optimal conditions.
-    \item Light pollution and equipment limitations introduced variability, leading to slightly higher error margins compared to professional datasets.
-    \item Cross-validation with professional data confirmed the overall reliability of the amateur observations, with minor deviations attributed to observational conditions.
-\end{itemize}
-Figures and tables summarizing the comparative results are presented below.
-
-% This study highlights the potential of amateur astronomers to contribute to the broader astronomical community.
-By focusing on specific systems like U Cephei, amateurs can provide valuable data to supplement professional observations.
-Future efforts should aim to enhance equipment calibration techniques and explore automated tools for improving data reliability.
-
-\section{Discussion}
+\subsection{Figure 3}
 

### 2025-01-08 python-scripts/plot-differences/main.py

@@ -32,7 +32,7 @@ plt.plot(tess_normalized_time, ucep_interp_mag, label='Personal Data from Montpe
 
 # Customize plot
 plt.gca().invert_yaxis()  # Magnitudes are inverted (brighter is lower)
-plt.xlabel('Time')
+plt.xlabel('Unix Time (normalized to 0)')
 plt.ylabel('Magnitude')
 plt.title('U Cephei Light Curve Comparison from TESS and Personal Data')
 plt.legend()

### 2025-01-15 paper.tex
docs
Signed-off-by: Thomas Mauran <thomasmauran@yahoo.com>

@@
 One thing we see when looking at those light curves is the fact they are not overlapping.
-This can be explained by the fact that TESS is in space and doesn't have to deal with the atmosphere, making the star looks brighter.
+This can be explained because TESS is in space and doesn't have to deal with the atmosphere, making the star looks brighter.
 It could also be explained by the fact
@@
 \subsection{Figure 3}
+
+To have a better comparison I shifted the amateur data by -0.5, this way both light curves are overlapping.
+This shift allows us to see that the light curves are following the same path but that the amateur data is just a bit dimmer than the TESS data.
+The variation of magnitude is different which is something I cannot explain. Even if my data is less precise in theory the variation of magnitude should be the same, but it is not the case here.
+
+This might be explained by a difference of sensitivity of the sensors used, or by the fact that the data was not normalized correctly, but this is something that needs to be investigated further.
 

### 2025-01-24 paper.tex
feat: biblio
Signed-off-by: Thomas Mauran <thomasmauran@yahoo.com>

@@
 \section{Conclusion}
-The personal photometric observations of U Cephei conducted in this study illustrate the potential for amateur astronomers to achieve a high degree of precision, even in light-polluted environments.
-These observations, while slightly less precise than professional datasets, offer valuable insights and demonstrate the viability of citizen science in advancing binary star research.
-Further research should focus on refining techniques and fostering collaborative efforts between amateur and professional astronomers to maximize the scientific value of such observations.
+The personal photometric observations of U Cephei conducted in this study illustrate the potential for amateur astronomers to achieve a high degree of precision, 
+even in light-polluted environments. These observations, while slightly less precise than professional datasets, 
+offer valuable insights and demonstrate the viability of citizen science in advancing binary star research. 
+Further research should focus on determining why we have a magnitude variation difference between the amateur and professional data,
+therefore we could get data from less polluted areas to see if the difference is due to the light pollution or to the equipment used.
 
 % References
-\begin{thebibliography}{99}
-\bibitem{example1} Smith, J., "Photometric Studies of Binary Stars," \textit{Astrophysical Journal}, vol. 123, no. 4, pp. 567-578, 2020.
-\bibitem{example2} Brown, A., \textit{Amateur Contributions to Astronomy}, Cambridge University Press, 2018.
-\bibitem{example3} Doe, R., "Comparative Analysis of Amateur and Professional Astronomical Data," \textit{Astronomy and Astrophysics}, vol. 456, no. 3, pp. 234-245, 2019.
+\begin{thebibliography}{9}
+
+    \bibitem{TESS}
+    NASA TESS Mission,
+    \textit{The Transiting Exoplanet Survey Satellite (TESS)}, 
+    \url{https://www.nasa.gov/tess}, accessed January 2025.
+
+    \bibitem{AAVSO}
+    American Association of Variable Star Observers,
+    \textit{Variable Star Charts, Data and Resources}, 
+    \url{https://www.aavso.org}, accessed January 2025.
+
+    \bibitem{Siril}
+    Siril,
+    \textit{Free Astronomical Image Processing Software},
+    \url{https://siril.org/}, accessed January 2025.
+
+    \bibitem{AstroImageJ}
+    Collins, K. A., Kielkopf, J. F., Stassun, K. G., Hessman, F. V. (2017). 
+    \textit{AstroImageJ: Image Processing and Photometric Analysis Software for Astronomical Research}.
+    The Astronomical Journal, 153(2), 77.
+
+    \bibitem{LightPollution}
+    International Dark-Sky Association (IDA), 
+    \textit{Understanding Light Pollution}, 
+    \url{https://www.darksky.org}, accessed January 2025.
+
+    \bibitem{SatellitePhotometry}
+    Guinan, E. F., Engle, S. G., Devinney, E. J. (2014). 
+    \textit{A Satellite Constellation for Photometry and Monitoring of Variable Stars}. 
+    Journal of the American Association of Variable Star Observers, 42, 235. 
+    \url{https://ui.adsabs.harvard.edu/abs/2014JAVSO..42..235G/abstract}, accessed January 2025.
+
+    \bibitem{AmateurObservation}
+    Mobberley, M. (2010). 
+    \textit{Amateur Astronomer's Handbook}. 
+    Springer, Chapter 1. 
+    \url{https://link.springer.com/content/pdf/10.1007/978-1-4471-0055-3_1.pdf}, accessed January 2025.
+
+    \bibitem{AmateurContribution}
+    Mattei, J. A. (1990). 
+    \textit{The Contribution of Amateur Astronomers to the Study of Variable Stars}.
+    Proceedings of the International Astronomical Union, 125, 73. 
+    \url{https://www.cambridge.org/core/services/aop-cambridge-core/content/view/6E3175E20C284177D4F534F506B1DD3E/S0252921100092794a.pdf/the-contribution-of-amateur-astronomers-to-the-study-of-variable-stars.pdf}, accessed January 2025.
+
+    \bibitem{VariableStar}
+Wikipedia,
+\textit{Variable Star}, 
+\url{https://en.wikipedia.org/wiki/Variable_star}, accessed January 2025.
+
     \end{thebibliography}
-
 \end{document}

### 2025-01-26 paper.tex
fix
Signed-off-by: Thomas Mauran <thomasmauran@yahoo.com>
fix: title
Signed-off-by: Thomas Mauran <thomasmauran@yahoo.com>

@@
 \title{Assessing the Scientific Value of Amateur Photometric Observations of Binary Star Transits}
-\author{Thomas Mauran \\\small Polytech Montpellier  \\\small thomas.mauran@etu.umontpellier.fr}
+\author{Thomas Mauran \\\small Université de Montpellier, Polytech Montpellier \\\small thomasmauran@yahoo.com}
 \date{\today}
@@
 This paper investigates the precision and reliability of photometric observations of binary star transits conducted by amateur astronomers compared to data collected by professional observatories.
-We analyze case studies, compare methodologies, and assess the implications for collaborative scientific research.
+We analyze case studies, compare the collected data to professional ones to measure the accuracy of the observations.
 \end{abstract}
@@
 observations in comparison to professional datasets, exploring the potential for collaboration
-and the challenges inherent in combining data from diverse sources. The final goal of the study if it is 
-successful enough is to submit the collected data to the AAVSO (American Association of Variable Star Observers).
+and the challenges inherent in combining data from diverse sources.
 

### 2025-02-01 paper.tex
docs: improve with feedbacks
Signed-off-by: Thomas Mauran <thomasmauran@yahoo.com>

@@
 In recent years, the field of astronomy has witnessed a growing collaboration between amateur 
-and professional astronomers. The advent of high-quality, low-cost equipment has enabled 
-amateur astronomers to perform sophisticated observations, including photometric studies of 
+and professional astronomers \cite{AmateurContribution}. The advent of high-quality, low-cost equipment has enabled 
+amateur astronomers to perform sophisticated observations \cite{AmateurObservation}, including photometric studies of 
 binary star transits. This paper focuses on photometric observations of the U Cephei 
@@
 To address the research question, this study employs a comparative analysis of photometric data.
-Observations of the U Cephei binary star system were conducted using personal equipment under urban light pollution conditions (Bortle 7).
+Observations of the U Cephei binary star system were conducted using personal equipment under urban light pollution conditions (Bortle 7) \cite{LightPollution}.
 The following steps were undertaken:
@@
 Specifying the equipment used in the study is essential to understanding the context and limitations of the observations. 
-I employed the following equipment for the photometric observations of U Cephei:
+We employed the following equipment for the photometric observations of U Cephei:
 
@@
     \item Autoguider: ZWO ASI 120MM mini monochrome camera and 50mm guide scope for guiding.
-    \item Software: N.I.N.A for image acquisition and PHD2 guiding software for tracking. AstroImageJ for data analysis and Siril for aligning the images.
+    \item Software: N.I.N.A for image acquisition and PHD2 guiding software for tracking. AstroImageJ \cite{AstroImageJ} for data analysis and Siril \cite{Siril} for aligning the images.
     \item Light Pollution: Montpellier, Bortle 7 (suburban/urban transition) location with moderate light pollution.
@@
 
-I chose manually the stars and took them because they have a known magnitude, allowing the software to guess the magnitude of U Cephei.
-To know the magnitude of those reference stars I used the \href{https://apps.aavso.org/vsp/chart/?star=U+Cep&fov=120.0&maglimit=12.0}{AAVSO website} which is a great tool to get information about stars and their magnitude.
+We chose manually the stars and took them because they have a known magnitude, allowing the software to guess the magnitude of U Cephei.
+To know the magnitude of those reference stars we used the \href{https://apps.aavso.org/vsp/chart/?star=U+Cep&fov=120.0&maglimit=12.0}{AAVSO website} \cite{AAVSO} which is a great tool to get information about stars and their magnitude.
 
@@
 
-After cleaning the data I wanted to see if it was possible to detect the transit event just by creating a video of the frames.
-Since this eclipse variation of magnitude is so important I felt like it could be visible enough.
+After cleaning the data we wanted to see if it was possible to detect the transit event just by creating a video of the frames.
+Since this eclipse variation of magnitude is so important we felt like it could be visible enough.
 
@@
 
-Using a python script I converted each of the fit file into a grayscale png and then was able to use the ffmpeg library to create a video of the frames.
+Using a python script we converted each of the fit file into a grayscale png and then was able to use the ffmpeg library to create a video of the frames.
 The result is available \href{https://youtube.com/shorts/rVnEccCb3Aw}{here}.
@@
 
-To validate the reliability of the amateur observations, I conducted a comparative analysis with professional data from the Transiting Exoplanet Survey Satellite (TESS) mission.
+To validate the reliability of the amateur observations, we conducted a comparative analysis with professional data from the Transiting Exoplanet Survey Satellite (TESS) mission \cite{TESS}.
 
@@
 
-This graphs shows the light curve of U Cephei from the TESS data in blue and the amateur data I collected in orange. 
+This graphs shows the light curve of U Cephei from the TESS data in blue and the amateur data we collected in orange. 
 Both curves display a parabolic similar shape.
@@
 
-\subsection{Figure 1}
+\subsection{Interpretation of the U Cephei Light Curve}
 
@@
 
-To understand a bit more those scales I think it is important to take the time to explain each of them.
+This light curve is displayed in the figure \ref{fig:light_curve} figure.
+
+To understand a bit more those scales we think it is important to take the time to explain each of them.
 \begin{itemize}
@@
 
-\subsection{Figure 2}
-One thing we see when looking at those light curves is the fact they are not overlapping.
+\subsection{Comparative Analysis of amateur and professional data}
+
+As described in the figure \ref{fig:tess-data-comparison}, one thing we see when looking at those light curves is the fact they are not overlapping.
 This can be explained because TESS is in space and doesn't have to deal with the atmosphere, making the star looks brighter.
@@
 
-\subsection{Figure 3}
+\subsubsection{Comparative Analysis with magnitude shift}
 
-To have a better comparison I shifted the amateur data by -0.5, this way both light curves are overlapping.
+To have a better comparison we shifted the amateur data by -0.5 in the figure \ref{fig:tess-data-comparison-shifted}, this way both light curves are overlapping.
 This shift allows us to see that the light curves are following the same path but that the amateur data is just a bit dimmer than the TESS data.
-The variation of magnitude is different which is something I cannot explain. Even if my data is less precise in theory the variation of magnitude should be the same, but it is not the case here.
+The variation of magnitude is different which is something we cannot explain. Even if my data is less precise in theory the variation of magnitude should be the same, but it is not the case here.
 
@@
 
-    \bibitem{AstroImageJ}
-    Collins, K. A., Kielkopf, J. F., Stassun, K. G., Hessman, F. V. (2017). 
-    \textit{AstroImageJ: Image Processing and Photometric Analysis Software for Astronomical Research}.
-    The Astronomical Journal, 153(2), 77.
-
     \bibitem{LightPollution}
-    International Dark-Sky Association (IDA), 
-    \textit{Understanding Light Pollution}, 
-    \url{https://www.darksky.org}, accessed January 2025.
-
-    \bibitem{SatellitePhotometry}
-    Guinan, E. F., Engle, S. G., Devinney, E. J. (2014). 
-    \textit{A Satellite Constellation for Photometry and Monitoring of Variable Stars}. 
-    Journal of the American Association of Variable Star Observers, 42, 235. 
-    \url{https://ui.adsabs.harvard.edu/abs/2014JAVSO..42..235G/abstract}, accessed January 2025.
+    Light Pollution Map, 
+    \textit{Interactive Light Pollution Map}, 
+    \url{https://www.lightpollutionmap.info/}, accessed January 2025.
 

### 2025-02-04 paper.tex
docs: improvements and finish of 4.4
Signed-off-by: Thomas Mauran <thomasmauran@yahoo.com>

@@
     \includegraphics[width=1\textwidth]{assets/star-transits.jpg}
-    \caption{Transit of binary star system schema and associated light curves.}
+    \caption{Transit of binary star system schema and associated light curves. \cite{VariableStar}}
     \label{fig:transits}
@@
 
-The first exoplanet was discovered using the transit method, and it's still one of the most used methods to detect exoplanets.
-One of the way to know if a star is part of a binary system is to observe it and see if it's light intensity varies over time, which can be a sign of a transit event.
+The first exoplanet was discovered using the transit method, and it is still one of the most used methods to detect exoplanets.
+One of the way to know if a star is part of a binary system is to observe it and see if it is light intensity varies over time, which can be a sign of a transit event.
 
@@
 
-There are multiple reasons why U Cephei is a great candidate for me in this study.
-
 \subsubsection{Period}
@@
 First of all U Cephei period is 2.493 days, which is quite short and allows for multiple chances to observe it on a short period of time. 
-Even though this period seems short since it's not exactly 3 days but 2 and a half it means that one observation out of 2 will be at night and the other during the day.
+Even though this period seems short since it is not exactly 3 days but 2 and a half it means that one observation out of 2 will be at night and the other during the day.
 Making observation nights possible every 5 days.
@@
 
-Secondly, this system eclipse is short, lasting only a couple of hours it's possible in one night to observe the complete eclipse, which is not the case for all binary systems.
+Secondly, this system eclipse is short, lasting only a couple of hours it is possible in one night to observe the complete eclipse, which is not the case for all binary systems.
 
@@
 
-In other words, during the transit, U Cephei will be 10 times dimmer than when it's not in transit. This is a huge variation and makes it easier to detect the transit.
+In other words, during the transit, U Cephei will be 10 times dimmer than when it is not in transit. This is a huge variation and makes it easier to detect the transit.
 
@@
 
+The observation procedure involved capturing images of the U Cephei binary star system and its comparison stars over a whole night, taking 20s exposures every 2 minutes.
+The observation was conducted on a clear night of 24th december with good seeing conditions to minimize atmospheric distortion.
+
 \subsection{Cleaning the amateur data}
@@
 \bigskip
-
-% TODO : Add a before and after image of the data cleaning process
 
@@
     \includegraphics[width=1\textwidth]{assets/aligned.png}
-    \caption{Cleaned data of U Cephei and it's comparison stars used for the study.}
+    \caption{Cleaned data of U Cephei and it is comparison stars used for the study.}
     \label{fig:cleaned_data}
@@
     \includegraphics[width=0.8\textwidth]{assets/ucep-stars-mag.png}
-    \caption{AAVSO Star chart of U Cephei and neighbors star magnitudes.}
+    \caption{AAVSO Star chart of U Cephei and neighbors star magnitudes.} \cite{AVVSOVariableStarPlotter}
     \label{fig:Ucep-stars-chart}
@@
 
-It's important to note something else in the \ref{fig:cleaned_data} image, we see that the frame has been shifted, this is what Siril did to make sure each frame is aligned.
+it is important to note something else in the figure \ref{fig:cleaned_data}, we see that the frame has been shifted, this is what Siril did to make sure each frame is aligned.
 
@@
 
-\subsection{Standardization of Data Formats, light curves and comparative analysis}
+To compare the amateur data with professional observations, we obtained light curves of U Cephei from the Transiting Exoplanet Survey Satellite (TESS) mission \cite{TESS}.
+The TESS data was processed and analyzed using python scripts which are available in this paper git repository \cite{GitRepository}.
+
+One of the most useful tools used during this process was the opensource software \href{https://www.tessextractor.app/}{TESS Extractor} \cite{TessExtractor} which allows to easily extract data from the TESS mission and create light curves.
+
+After the dataset was extracted we were able to compare the amateur data to the professional one, we had to make sure that the data was aligned correctly.
+
+Over the years variations of the period of U Cephei have been observed \cite{CEPU} \cite{PeriodChanges}, which is why we had to choose recent data to make sure the period was the same as the one we observed.
 
@@
 \section{Results}
+
+In this part we will present the results of the study, starting with the light curve of U Cephei and then comparing it to the professional data.
 
@@
 This is another light curve comparison very similar to the previous one, but this time the amateur data has been shifted by -0.5.
-
-% This study highlights the potential of amateur astronomers to contribute to the broader astronomical community.
-By focusing on specific systems like U Cephei, amateurs can provide valuable data to supplement professional observations.
-Future efforts should aim to enhance equipment calibration techniques and explore automated tools for improving data reliability.
 
@@
 
+    \bibitem{AVVSOVariableStarPlotter}
+    AVVSO VariableStarPlotter,
+    \textit{AVVSO VariableStarPlotter}, 
+    \url{https://apps.aavso.org/vsp/chart/?star=U+Cep&fov=120.0&maglimit=12.0}, accessed January 2025.
+
+    \bibitem{GitRepository}
+    Git Repository,
+    \textit{Git repository}, 
+    \url{https://github.com/thomas-mauran/research-paper}, accessed January 2025.
+
+    \bibitem{TessExtractor}
+    Tess Extractor,
+    \textit{Tess Extractor}, 
+    \url{https://www.tessextractor.app/}, accessed January 2025.
+
+    \bibitem{CEPU}
+    J.M. Kreiner, 2004, Acta Astronomica, vol. 54, pp 207-210,
+    \textit{J.M. Kreiner, 2004, Acta Astronomica, vol. 54, pp 207-210}, 
+    \url{https://www.as.up.krakow.pl/minicalc/CEPU.HTM}, accessed January 2025.
+
+    \bibitem{PeriodChanges}
+    OLSON, E. C., CRAWFORD, R. C., HALL, D. S., LOUTH, H., MARKWORTH, N. L., PIIROLA, V. (1981). FURTHER PERIOD CHANGES IN U CEPHEI. 
+    \textit{Publications of the Astronomical Society of the Pacific}, 93(554), 464–469.  
+    \url{http://www.jstor.org/stable/40677799}, accessed January 2025.
+
     \end{thebibliography}

### 2025-02-05 paper.tex
fix: typo
Signed-off-by: Thomas Mauran <thomasmauran@yahoo.com>

@@
 
-U Cephei is a very interesting binary star system and a great pick to try catching transit eclipses.
+U Cephei is a very interesting binary star system and a great pick to try catching transit eclipses for multiple reasons
 
@@
 
-First of all U Cephei period is 2.493 days, which is quite short and allows for multiple chances to observe it on a short period of time. 
+First of all U Cephei period is 2.493 days \cite{VariableStar}, which is quite short and allows for multiple chances to observe it on a short period of time. 
 Even though this period seems short since it is not exactly 3 days but 2 and a half it means that one observation out of 2 will be at night and the other during the day.
